On the entropy of isothermal dusty gas: application to protoplanetary disks

### 2016-08-02 model.tex
adding fixZ results
new vshear figs

In practice, we consider $\epsilon_0 \ll 1$ and settled dust such that
$\Htilde<\Hgas$. Then $\rhog(r,z)$ is effectively Gaussian, as in the
dust-free case. The dust density is approximately 
\begin{align}
  \rhod \simeq \epsilon_0\rho_\mathrm{g0}(r) \exp
        {\left(-\frac{z}{2H_\mathrm{d}^2}\right)}, 
\end{align}
with 
\begin{align}
  \frac{1}{H_\mathrm{d}^2} = \frac{1}{\Htilde^2} + \frac{1}{\Hgas^2}, 
\end{align}
and $H_\mathrm{d}$ is the dust-scale height. In numerical
calculations, we  we specify $H_\mathrm{d}< \Hgas$ to obtain 
$\Htilde$ for input.

>>>>

We usually consider $\epsilon_0 \ll 1$ and settled dust such that
$\Htilde<\Hgas$. Then $\rhog(r,z)$ is effectively Gaussian, as in the
dust-free case. The dust density is approximately 
\begin{align}
  \rhod \simeq \epsilon_0\rho_\mathrm{g0}(r) \exp
        {\left(-\frac{z^2}{2H_\mathrm{d}^2}\right)}, 
\end{align}
with 
\begin{align}
  \frac{1}{H_\mathrm{d}^2} = \frac{1}{\Htilde^2} + \frac{1}{\Hgas^2}, 
\end{align}
and $H_\mathrm{d}$ is the dust-scale height. In numerical
calculations, we  we specify $H_\mathrm{d}< \Hgas$ to obtain 
$\Htilde$ for input.

Finally, we define 
\begin{align}
  Z \equiv \epsilon_0\frac{\Hd}{\Hg} \simeq
  \frac{\Sigma_\mathrm{d}}{\Sigma_\mathrm{g}} 
\end{align}
as a proxy of the ratio between the dust surface density
$\Sigma_\mathrm{d}$ and the gas surface density $\Sigma_\mathrm{g}$.

### 2016-08-02 result.tex
adding fixZ results
new vshear figs

@@

\begin{figure}
  \includegraphics[scale=0.54, clip=true, trim=0cm 2.5cm 0cm 0cm]{figures/result2d_dg1d-3.ps}\\
  \includegraphics[scale=0.54]{figures/result2d_dg1.ps} 
  \caption{Fundamental dusty VSI mode in real space for midplane dust-to-gas
    ratio $\epsilon_0=10^{-3}$ (top) and $\epsilon_0=1$
    (bottom). The color scale shows the perturbation to the
    dust-to-gas ratio, $\delta\epsilon$; and the arrows show
    $\sqrt{\rho}\left(\dd v_x, \dd v_z\right)$. 
    \label{vsi_dust_loading2d}
    }
\end{figure}

@@

\subsection{Fixed metalicity} 
Here we vary the dust layer thickness $\Hd$ but hold 
\begin{align}\label{metalicity_def}
Z \equiv \epsilon_0 \Htilde = \text{constant,}
\end{align}
so that $\Sigma_\mathrm{d}/\Sigma_\mathrm{g}$ is
fixed. Eq. \ref{metalicity_def} then gives the required midplane
dust-to-gas ratio.

@@

\begin{figure}
  \includegraphics[width=\linewidth]{figures/compare_vshear_fixZ} 
  \caption{Vertical shear rate in a locally isothermal, dusty disk
    with fixed dust-to-gas mass and dust thickness $\Hd=0.1\Hg$
    (black) and $\Hd=0.99\Hg$ (blue). 
    \label{compare_vshear_fixZ}
    }
\end{figure}

\begin{figure}
  \includegraphics[scale=0.33, clip=true, trim=0.5cm 0cm 3cm 0cm]{figures/result2d_Hd1.ps}\includegraphics[scale=0.33, clip=true, trim=2cm 0cm 0cm 0cm]{figures/result2d_Hd0d1.ps} 
  \caption{
%dusty VSI mode in real space for midplane dust-to-gas
%    ratio $\epsilon_0=10^{-3}$ (top) and $\epsilon_0=1$
%    (bottom). The color scale shows the perturbation to the
%    dust-to-gas ratio, $\delta\epsilon$; and the arrows show
%    $\sqrt{\rho}\left(\dd v_x, \dd v_z\right)$. 
    stuff
    \label{result2d_fixZ}
    }
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\linewidth]{figures/compare_vshear_Nz2_fixHd} 
  \caption{Vertical shear rate (solid) compared to vertical buoyancy (dotted) in a locally isothermal, dusty disk
    with dust thickness $\Hd=0.99\Hg$ and midplane dust-to-gas ratio
    of $\epsilon_0=10^{-3}$ (black) and $\epsilon_0=1$ (blue). 
    \label{compare_vshear_fixHd}
    }
\end{figure}

@@

\begin{figure}
%  \includegraphics[scale=0.54, clip=true, trim=0cm 2.5cm 0cm 0cm]{figures/result2d_dg1d-3.ps}\\
%  \includegraphics[scale=0.54]{figures/result2d_dg1.ps} 
\includegraphics[scale=0.32, clip=true, trim=0.5cm 0cm 3cm 0cm]{figures/result2d_dg1d-3.ps}\includegraphics[scale=0.32, clip=true, trim=1.8cm 0cm 0cm 0cm]{figures/result2d_dg1.ps}
  \caption{Fundamental dusty VSI mode in real space for midplane dust-to-gas
    ratio $\epsilon_0=10^{-3}$ (top) and $\epsilon_0=1$
    (bottom). The color scale shows the perturbation to the
    dust-to-gas ratio, $\delta\epsilon$; and the arrows show
    $\sqrt{\rho}\left(\dd v_x, \dd v_z\right)$. 
    \label{vsi_dust_loading2d}
    }
\end{figure}

@@

\subsection{Fixed metalicity} 
Here we vary the dust layer thickness $\Hd$ but hold 
$Z \equiv \epsilon_0 \Htilde = \text{constant,}$ 
so that $\Sigma_\mathrm{d}/\Sigma_\mathrm{g}$ is
fixed. This gives the required midplane dust-to-gas ratio.

@@

\begin{figure}
  \includegraphics[width=\linewidth]{figures/compare_vshear_Nz2_fixZ} 
  \caption{Vertical shear rate (solid) compared to vertical buoyancy (dotted) in a locally isothermal, dusty disk
    with fixed dust-to-gas mass ratio $Z=0.03$ and dust thickness $\Hd=0.1\Hg$
    (black) and $\Hd=0.99\Hg$ (blue). 
    \label{compare_vshear_fixZ}
    }
\end{figure}

\begin{figure}
  \includegraphics[scale=0.32, clip=true, trim=0.5cm 0cm 3cm 0cm]{figures/result2d_Hd1.ps}\includegraphics[scale=0.32, clip=true, trim=1.8cm 0cm 0cm 0cm]{figures/result2d_Hd0d1.ps} 
  \caption{
%dusty VSI mode in real space for midplane dust-to-gas
%    ratio $\epsilon_0=10^{-3}$ (top) and $\epsilon_0=1$
%    (bottom). The color scale shows the perturbation to the
%    dust-to-gas ratio, $\delta\epsilon$; and the arrows show
%    $\sqrt{\rho}\left(\dd v_x, \dd v_z\right)$. 
    stuff
    \label{result2d_fixZ}
    }
\end{figure}
